Build azimuth compatible fetal kidney reference from the kidney cell atlas

### 2024-08-09 analyses/cell-type-wilms-tumor-06/00_fetal_reference_kidney.Rmd
Update analyses/cell-type-wilms-tumor-06/00_fetal_reference_kidney.Rmd
Co-authored-by: Jaclyn Taroni <19534205+jaclyn-taroni@users.noreply.github.com>

---
title: "Build azimuth compatible fetal kidney reference from the kidney cell atlas"
author: "Maud PLASCHKA"
date: '2024-08-07'
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

```{r cfg}
cfg = list()
cfg$padj_thershold = 0.05
cfg$lfc_threshold = 1
cfg$rate1_threshold = 0.5

set.seed(12345)
```

>>>>

---
title: "Build azimuth compatible fetal kidney reference from the kidney cell atlas"
author: "Maud PLASCHKA"
date: '2024-08-07'
params:
  ref_url: "https://datasets.cellxgene.cziscience.com/40ebb8e4-1a25-4a33-b8ff-02d1156e4e9b.rds"
  padj_threshold: 0.05
  lfc_threshold: 1
  rate1_threshold: 0.5
  seed: 12345
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

```{r cfg}
cfg <- list()
cfg$padj_threshold <- params$padj_threshold
cfg$lfc_threshold <- params$lfc_threshold
cfg$rate1_threshold <- params$rate1_threshold

set.seed(params$seed)
```
